Dirac neutrino mass generation from Majorana messenger

### 2019-09-16 draft.tex
mc

With the aim of thermalize the right-handed neutrinos we consider an extension of the previous setup by introducing additional chiral SM singlet fields and assigning nonzero $\operatorname{U}(1)_X$ charges to the SM fields. 
%A not-so-minimal model can be obtained by introducing additional chiral SM singlet fields. 
In this case we can use the solutions to the anomaly cancellation conditions found for a general  Abelian gauge symmetry $\operatorname{U(1)}_X$ with generation-independent charge assignments in Refs.~\cite{Jenkins:1987ue,Appelquist:2002mw,Campos:2017dgc,1504.06291,Okada:2018tgy,Jana:2019mez}, where the previous dark symmetry denoted as $X=\mathcal{D}$ corresponds to the fermiophobic setup~\cite{Campos:2017dgc,Bertuzzo:2018itn,Bertuzzo:2018ftf}.

@@

\section{Collider constraints}
The recasting of the latest ATLAS results for the search of dilepton resonances using $139\ \text{fb}^{-1}$~\cite{Aad:2019fac} was done
in~\cite{Chiang:2019ajm} for the $\operatorname{U}(1)_{B-L}$ model.
The green (upper) region in fig.~\ref{fig:u1blc} shows the excluded region at $95\%\ \text{C.L.}$ To ease the comparison with other results, we show the exclusion as function of $M_{Z'}/g_{BL}$. In particular, the limit from LEP for $\operatorname{U}(1)_{B-L}$ model is~\cite{hep-ph/0408098,Heeck:2014zfa}\footnote{The constraint as function of $h=-1-l$ is given in~\cite{1611.02672}. }, 
\begin{align}
  M_{Z'}/g_{BL}>6.7\ \text{TeV}\,,&&\text{at $95\%$ C.L }\,,
\end{align}
which is obtained from the search for effective four-lepton operators and is valid for $M_{Z'}\gg 200\ \text{GeV}$. This constraint corresponds to the excluded magenta (lower) region of fig.~\ref{fig:u1blc} and start to be relevant for $M_{Z'}>5.8\ \text{TeV}$.

@@

\appendix
\section{Anomaly cancellation}
We use $f$ ($f$) to denote the general $\operatorname{U}(1)_X$ generation-independent charge assignments of the field $f_R$ ($F_L$). The three linear anomalies in $\operatorname{U(1)_X}$ allows to express three $X$-charges in terms of the other two
\begin{align}
  u=&-e+\frac{2l}{3}\,,& d=& e-\frac{4l}{3}\,,& q=& -\frac{l}{3}\,.
\end{align}
The quadratic anomaly condition is automatically satisfied, while the mixed gauge-gravitational and cubic anomalies depend of any extra singlet quiral fermions of zero hypercharge, like the right-handed counterpart of the Dirac neutrinos. For $N$ extra quiral fields with $X$-charge $n_{\alpha}$, these conditions read
\begin{align}
  \sum_{\alpha=1}^N n_{\alpha}+3 (e-2l)=&0\,, &   \sum_{\alpha=1}^N n_{\alpha}^3+3 (e-2l)^3=&0\,. &
\end{align}
There are many known solutions for the case in which $e-2l=1$, including the $N=3$ case $(-4,-4,+5)$~\cite{Appelquist:2002mw}. The full set of standard model charges in terms of $l$ is just
\begin{align}
  u=&-1-\frac{4l}{3}\,,&d=&1+\frac{2l}{3}\,,&q=&-\frac{l}{3}\,,&e=&1+2l\,,&h=&-1-l\,.
  \label{Eq:SMCharges}
\end{align}
The same solution but in terms of $h$ () given in ~\cite{Jenkins:1987ue,1504.06291}.

>>>>

With the aim of thermalize the right-handed neutrinos we consider an extension of the previous setup by introducing additional chiral SM singlet fields and assigning nonzero $\operatorname{U}(1)_X$ charges to the SM fields. 
%A not-so-minimal model can be obtained by introducing additional chiral SM singlet fields. 
In this case we can use the solutions to the anomaly cancellation conditions found for a general  Abelian gauge symmetry $\operatorname{U(1)}_X$ with generation-independent charge assignments in Refs.~\cite{Jenkins:1987ue,Appelquist:2002mw,Campos:2017dgc,Oda:2015gna,Okada:2018tgy,Jana:2019mez}, where the previous dark symmetry denoted as $X=\mathcal{D}$ corresponds to the fermiophobic setup~\cite{Campos:2017dgc,Bertuzzo:2018itn,Bertuzzo:2018ftf}.

@@

\section{Collider constraints}
The recasting of the latest ATLAS results for the search of dilepton resonances using $139\ \text{fb}^{-1}$~\cite{Aad:2019fac} was done
in~\cite{Chiang:2019ajm} for the $\operatorname{U}(1)_{B-L}$ model.
The green (upper) region in fig.~\ref{fig:u1blc} shows the excluded region at $95\%\ \text{C.L.}$ To ease the comparison with other results, we show the exclusion as function of $M_{Z'}/g_{BL}$. In particular, the limit from LEP for $\operatorname{U}(1)_{B-L}$ model is~\cite{Carena:2004xs,Heeck:2014zfa}\footnote{The constraint as function of $h=-1-l$ is given in~\cite{Okada:2016tci}. }, 
\begin{align}
  M_{Z'}/g_{BL}>6.7\ \text{TeV}\,,&&\text{at $95\%$ C.L }\,,
\end{align}
which is obtained from the search for effective four-lepton operators and is valid for $M_{Z'}\gg 200\ \text{GeV}$. This constraint corresponds to the excluded magenta (lower) region of fig.~\ref{fig:u1blc} and start to be relevant for $M_{Z'}>5.8\ \text{TeV}$.

@@

\appendix
\section{Anomaly cancellation}
We use $f$ ($f$) to denote the general $\operatorname{U}(1)_X$ generation-independent charge assignments of the field $f_R$ ($F_L$). The three linear anomalies in $\operatorname{U(1)_X}$ allows to express three $X$-charges in terms of the other two
\begin{align}
  u=&-e+\frac{2l}{3}\,,& d=& e-\frac{4l}{3}\,,& q=& -\frac{l}{3}\,.
\end{align}
The quadratic anomaly condition is automatically satisfied, while the mixed gauge-gravitational and cubic anomalies depend of any extra singlet quiral fermions of zero hypercharge, like the right-handed counterpart of the Dirac neutrinos. For $N$ extra quiral fields with $X$-charge $n_{\alpha}$, these conditions read
\begin{align}
  \sum_{\alpha=1}^N n_{\alpha}+3 (e-2l)=&0\,, &   \sum_{\alpha=1}^N n_{\alpha}^3+3 (e-2l)^3=&0\,. &
\end{align}
There are many known solutions for the case in which $e-2l=1$, including the $N=3$ case $(-4,-4,+5)$~\cite{Appelquist:2002mw}. The full set of standard model charges in terms of $l$ is just
\begin{align}
  u=&-1-\frac{4l}{3}\,,&d=&1+\frac{2l}{3}\,,&q=&-\frac{l}{3}\,,&e=&1+2l\,,&h=&-1-l\,.
  \label{Eq:SMCharges}
\end{align}
The same solution but in terms of $h$ () given in ~\cite{Jenkins:1987ue,Oda:2015gna}.
